---
title: "linreg"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{linreg}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(Lab4AroEnPonOl)
```

## Lab4AroEnPonOl
The Lab4AroEnPonOl package contains the function linreg(). This function performs least sqaures linear regression using the formula on the dataset given. Run ??linreg for more information on the output.
linreg() implements linear regression through the QR decomposition and outputs an S3 object with methods implemented for pred(), plot(), print(), resid() and summary(). 

```{r}
model <- linreg(formula = Sepal.Length ~ Sepal.Width + Petal.Length, data = iris[-c(1:5), ])
```

Summary summarizes the estimated coefficients, Beta and their standard errors, SE. 

```{r}
summary(model)
```
resid() and residuals() return the residuals $\varepsilon=y-\hat{y}$ for the model.
```{r}
resid(model)[1:3]
residuals(model)[1:3]
```

plot() creates residualplots that can be used to study the performance and the models assumptions. Standardised residuals are calculated via $standardized\ residuals = \frac{\varepsilon}{\hat{\sigma_\varepsilon}}$. Where $\hat{\sigma_\varepsilon}^2 = \frac{\Sigma\varepsilon_i^2}{n-p}$.
```{r}
plot(model)
```

Print and coef are very similar, but coef returns a vector while print does not.
```{r}
print(model)
coef(model)
```
pred() and predict() uses the estimated coefficients to make predictions for new data.
```{r}
pred(model, iris[1:3, ])
predict(model, iris[1:3, ])
```
